---
title: "Alcohol vs Seat choice"
author: "Hailey Watkins-oliver"
date: "Fall 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data


## Now add in boxplot

```{r}
boxplot(alcohol~Seat,data=davisdata)
```

The boxes are not disjoint. The median of the box is higher than the front and middle box. The front and middle box are similar in size but there are more outlines in the middle box. 




## Numerical Summarys 



```{r}
favstats(momheight~Sex,data=ucdavis1)
```


When it comes to the amount of persons who are drinking, the back has more than twice as many as the front. According to this summary, the back seat could hold up to 55 drinks, which is twice as much as the front and middle seats combined, even though there were only 32 persons occupying it. The front seat has roughly two drinks, the rear seat has a median of about three, and the back seat has an average of 9.5 drinks.  

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

There is a one in ten thousand chance of receiving these outcomes. To determine which seats differ from the others, more research is now required.
```{r}
par(mar = c(3, 8.7, 2, 2))
plot(TukeyHSD(model1),las=2)
```


The rear and the front are not the same. While the front and middle are distinct from one another, they are not from the back. The front, center, and back are not the same thing.

## Conclusions

In conclusion what I got from this assighment is that the boxes are not disjoint. The middle of the box is higher than the front and center box. The front and center box are comparable in measure but there are more traces within the center box. Too when it comes to the sum of people who are drinking, the back has more than twice as numerous as the front. Concurring to this rundown, the back situate seem hold up to 55 drinks, which is twice as much as the front and center seats combined, indeed in spite of the fact that there were as it were 32 persons possessing it. There's  a one in ten thousand chance of getting these results. To decide which seats vary from the others, more inquire about is presently required. In conclusion, the raise and the front are not the same. Whereas the front and center are unmistakable from one another, they are not from the back. The front, center, and back are not the same thing.


